---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = F,
  warning = F,
  error = F,
  echo = F,
  comment = "#>"
)
library(targets)
library(DiagrammeR)
library(terra)
```

# Targets_Species_Community

<!-- badges: start -->
<!-- badges: end -->

The goal of Targets_Species_Community is to recreate the community generated but using the targets r package, here you can see the whole workflow


# Results

With 2500 species the whole workflow finished some mistakes in 3.078 hours. Here are the results in tifs



## Richness

```{r richnessplot}
tif_files_richness <- list.files("Results/Richness/", pattern = "\\.tif$", full.names = TRUE)
plot(terra::rast(tif_files_richness), colNA = "black")
```


## Phylogenetic diversity

```{r PDsplot}
tif_files_PD <- list.files("Results/PD/", pattern = "\\.tif$", full.names = TRUE)
plot(terra::rast(tif_files_PD), colNA = "black")
```

## Rarity

```{r Raritysplot}
tif_files_rarity <- list.files("Results/Rarity/", pattern = "\\.tif$", full.names = TRUE)
plot(terra::rast(tif_files_rarity), colNA = "black")
```


test mermaid

```{r, results = "asis", echo = FALSE}
cat(c("```{mermaid}", targets::tar_mermaid(targets_only = T, legend = F), "```"), sep = "\n")
```

```{mermaid}
graph LR
  style Graph fill:#FFFFFF00,stroke:#000000;
  subgraph Graph
    direction LR
    x9c6d1c6ff27855c7(["LanduseSuitability"]):::uptodate --> xd8b9f31c0822a52d(["LanduseTable"]):::uptodate
    xf4b68b9a0db047f1["Long_Buffer"]:::uptodate --> xd88abd50d7d969a8["Final_Presences"]:::uptodate
    x49cd1d3f69c871c0(["Long_LU_table"]):::uptodate --> xd88abd50d7d969a8["Final_Presences"]:::uptodate
    xbe15f87624992817(["LookUpTable"]):::uptodate --> xd88abd50d7d969a8["Final_Presences"]:::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> x6e7e15abd6323cf0["output_Rarity"]:::uptodate
    x7eea86b153654cc3["rarity"]:::uptodate --> x6e7e15abd6323cf0["output_Rarity"]:::uptodate
    x03de5d46cb8263bd(["Filter_Counts"]):::uptodate --> x1234c39602c1f6ea["Presences"]:::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> xb20884a1d0267e2d["output_Richness"]:::uptodate
    xc60fb40d268bec96["PhyloDiversity"]:::uptodate --> xb20884a1d0267e2d["output_Richness"]:::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> xc73d904d90e721c9["buffer_500"]:::uptodate
    x1234c39602c1f6ea["Presences"]:::uptodate --> xc73d904d90e721c9["buffer_500"]:::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> x54460dbf2d0d1aab["ModelAndPredict"]:::uptodate
    x1234c39602c1f6ea["Presences"]:::uptodate --> x54460dbf2d0d1aab["ModelAndPredict"]:::uptodate
    xd88abd50d7d969a8["Final_Presences"]:::uptodate --> x1ab2da0dbce80c54(["joint_final_presences"]):::uptodate
    xc73d904d90e721c9["buffer_500"]:::uptodate --> xf4b68b9a0db047f1["Long_Buffer"]:::uptodate
    x54460dbf2d0d1aab["ModelAndPredict"]:::uptodate --> xbe15f87624992817(["LookUpTable"]):::uptodate
    xa7956357d7f8182e["Thresholds"]:::uptodate --> xbe15f87624992817(["LookUpTable"]):::uptodate
    x1ab2da0dbce80c54(["joint_final_presences"]):::uptodate --> x7eea86b153654cc3["rarity"]:::uptodate
    x17bbde0022942793(["rarity_weight"]):::uptodate --> x7eea86b153654cc3["rarity"]:::uptodate
    x7ced752a37ed4412(["Only_Plants"]):::uptodate --> x991d57889963b22e["Count_Presences"]:::uptodate
    x76752fc0bd503faf(["Clean"]):::uptodate --> x7ced752a37ed4412(["Only_Plants"]):::uptodate
    x1ab2da0dbce80c54(["joint_final_presences"]):::uptodate --> x17bbde0022942793(["rarity_weight"]):::uptodate
    x03de5d46cb8263bd(["Filter_Counts"]):::uptodate --> x01fcaa42022f4a51(["Phylo_Tree"]):::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> x58fd9c294753b820["output_PD"]:::uptodate
    xc60fb40d268bec96["PhyloDiversity"]:::uptodate --> x58fd9c294753b820["output_PD"]:::uptodate
    xd8b9f31c0822a52d(["LanduseTable"]):::uptodate --> x49cd1d3f69c871c0(["Long_LU_table"]):::uptodate
    x991d57889963b22e["Count_Presences"]:::uptodate --> x03de5d46cb8263bd(["Filter_Counts"]):::uptodate
    x6d51284275156668(["file"]):::uptodate --> xb7119b48552d1da3(["data"]):::uptodate
    xfab3ac936a7a6fb3(["LandUseTiff"]):::uptodate --> xa7956357d7f8182e["Thresholds"]:::uptodate
    x54460dbf2d0d1aab["ModelAndPredict"]:::uptodate --> xa7956357d7f8182e["Thresholds"]:::uptodate
    x1234c39602c1f6ea["Presences"]:::uptodate --> xa7956357d7f8182e["Thresholds"]:::uptodate
    xd88abd50d7d969a8["Final_Presences"]:::uptodate --> x3295ae898e560fa5(["Richness"]):::uptodate
    x1ab2da0dbce80c54(["joint_final_presences"]):::uptodate --> xc60fb40d268bec96["PhyloDiversity"]:::uptodate
    x01fcaa42022f4a51(["Phylo_Tree"]):::uptodate --> xc60fb40d268bec96["PhyloDiversity"]:::uptodate
    xb7119b48552d1da3(["data"]):::uptodate --> x76752fc0bd503faf(["Clean"]):::uptodate
  end
  classDef uptodate stroke:#000000,color:#ffffff,fill:#354823;
  classDef none stroke:#000000,color:#000000,fill:#94a4ac;
```

